Intelligence and Age at First Intercourse: Cause or Confound?

### 2015-11-09 Manuscript/Manuscript.tex
changes

\documentclass[a4paper,man,apacite,natbib,12pt]{apa6}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

%%%%%%%%%%%% Title %%%%%%%%%%%%
\title{Intelligence and Age at First Intercourse: Cause or Confound?}
\shorttitle{Intelligence and AFI}

% Authors and Affliations
\author{S. Mason Garrison and Joseph Lee Rodgers}
\affiliation{Vanderbilt University}

% Author Note
\authornote{\input{../Common/content/title/authornote.txt}}

% Abstract
\abstract{Last compile was \today\ at \currenttime\\
%% Empirical Study
\input{../Common/content/title/abstract_empreport.txt}}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\maketitle
%
%%%%%%%%%%%% R %%%%%%%%%%%%

@@

%%%%%%%%%%%% Method %%%%%%%%%%%%
\section{Method}
% Research Design
\subsection{Research Design}
\input{../Common/content/method/design.txt}
%
% Sample
\subsection{Sample}
\input{../Common/content/method/subjects.txt}
%
% Tetrads
\subsection{Tetrads}
\input{../Common/content/method/tetrad.txt}
%
% Age at First Intercourse
\subsection{Age at First Intercourse}
\input{../Common/content/method/AFI.txt}
%
%%%%%%%%%%%% Measurement %%%%%%%%%%%%
\section{Measures}
%
% Gen1
\subsection{Generation 1}
\input{../Common/content/method/Gen1measures.txt}
%
% Gen2
\subsection{Generation 2}
\input{../Common/content/method/Gen2measures.txt}
%
% Difference Score Reliability
\subsection{Reliability of Difference Scores}
\input{../Common/content/method/diffscores.txt}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{lstlisting}[style=Rsettings]
sigmax = sqrt(1.1881)\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
sigmay = sigmax\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
rxx = .87\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
ryy = rxx\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
rxy=.67\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
r.diff.intelligence <- (sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) /
  (sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
r.diff.intelligence\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
## [1] 0.606
\end{lstlisting}
\end{kframe}
\end{knitrout}
The calculated reliability of Generation 1's differences in AFQT was 0.606, acceptable, but lower than the empirical correlation we derived for cousin differences.\\

We can also calculate the difference score reliability for Generation 2 AFI, by substituting the following values into equation \ref{equationLord1963},
where, \begin{itemize}
\item $\sigma_{x}^{2}$ and $\sigma_{y}^{2}$ are 4.41 (from Table \vref{table_summary_stats_sibinsampleg2}) %the variance of Gen2 Mean AFI, 
\item $\rho_{xx'}$ and $\rho_{yy'}$ are .76 (from Table \vref{table_measurement_trt_g1afi}), 
\item $\rho_{xy}$ is the AFI correlation between first born cousins is .099.(from Figure \vref{plot_between})\end{itemize}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{lstlisting}[style=Rsettings]
sigmax = sqrt(4.41)\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
sigmay = sigmax\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
rxx = .76\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
ryy = rxx\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
rxy=.099\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
r.diff.afi<-(sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) / 
  (sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
r.diff.afi\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
## [1] 0.734
\end{lstlisting}
\end{kframe}
\end{knitrout}
 Gen2 Mean AFI difference scores were also reliable (r = 0.734) and comparable to Generation 1 sibling differences.
%%%%%%%%%%%% Results %%%%%%%%%%%%
\section{Results}
\input{../Common/content/results/results.txt}
%
% Between Family
\subsection{Between Family}
\input{../Common/content/results/results_between.txt}
%
% Within Family
\subsection{Within Family}
\input{../Common/content/results/results_within.txt}
%
%%%%%%%%%%%% Discussion %%%%%%%%%%%%
\section{Discussion}
\input{../Common/content/discussion/discussion.txt}

@@

\end{knitrout}
\end{center}
\pagebreak
%
\begin{center}
\captionof{figure}{Between Family Correlations}
\label{plot_between}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=1.1\paperwidth]{figure/plot_corplotmatrix_between-1}

\end{knitrout}
\end{center}
\pagebreak
%
\begin{center}
\captionof{figure}{Within Family Correlations}
\label{plot_within}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=1.1\paperwidth]{figure/plot_corplotmatrix_within-1}

@@

>>>>

\documentclass[a4paper,man,apacite,natbib,12pt,longtable]{apa6}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

%%%%%%%%%%%% Title %%%%%%%%%%%%
\title{Intelligence and Age at First Intercourse: Cause or Confound?}
\shorttitle{Intelligence and AFI}
%
% Authors and Affiliations
\author{S. Mason Garrison and Joseph Lee Rodgers}
\affiliation{Vanderbilt University}
%
% Author Note
\authornote{\input{../Common/content/title/authornote.txt}}
%
% Abstract
\abstract{Last compile was \today\ at \currenttime\\
\input{../Common/content/title/abstract_empreport.txt}}
%
% Key Words
\keywords{Age at first intercourse; Cross-sectional data; Intelligence; Quasi-Experimental}
%
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\maketitle
%
%%%%%%%%%%%% R %%%%%%%%%%%%

@@

%%%%%%%%%%%% Method %%%%%%%%%%%%
\section{Method}
% Research Design
\subsection{Research Design}
\input{../Common/content/method/design.txt}
%
% Sample
\subsection{Sample}
\input{../Common/content/method/subjects.txt}
%
% Tetrads
\subsection{Tetrads}
\input{../Common/content/method/tetrad.txt}
%
% Age at First Intercourse
\subsection{Age at First Intercourse}
\input{../Common/content/method/AFI.txt}
%
%%%%%%%%%%%% Measurement %%%%%%%%%%%%
\section{Measures}
%
% Gen1
\subsection{Generation 1}
\input{../Common/content/method/Gen1measures.txt}
%
% Gen2
\subsection{Generation 2}
\input{../Common/content/method/Gen2measures.txt}
%
% Difference Score Reliability
\subsection{Reliability of Difference Scores}
\input{../Common/content/method/diffscores.txt}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{lstlisting}[style=Rsettings]
sigmax = sqrt(1.1881)\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
sigmay = sigmax\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
rxx = .87\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
ryy = rxx\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
rxy=.67\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
(sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) /
  (sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
## [1] 0.606
\end{lstlisting}
\end{kframe}
\end{knitrout}

The calculated reliability of Generation 1's differences in AFQT was 0.606, acceptable, but lower than the empirical correlation we derived for cousin differences.\\

We can also calculate the difference score reliability for Generation 2 AFI, by substituting the following values into equation \ref{equation_Lord1963},
where, \begin{itemize}
\item $\sigma_{x}^{2}$ and $\sigma_{y}^{2}$ are 4.41 (from Table \vref{table_summary_stats_sibinsampleg2}) %the variance of Gen2 Mean AFI, 
\item $\rho_{xx'}$ and $\rho_{yy'}$ are .76 (from Table \vref{table_measurement_trt_g1afi}), 
\item $\rho_{xy}$ is the AFI correlation between first born cousins is .099.(from Figure \vref{plot_between})\end{itemize}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{lstlisting}[style=Rsettings]
sigmax = sqrt(4.41)\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
sigmay = sigmax\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
rxx = .76\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
ryy = rxx\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
rxy=.099\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
(sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) / 
  (sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)\end{lstlisting}
\begin{lstlisting}[style=Rsettings]
## [1] 0.734
\end{lstlisting}
\end{kframe}
\end{knitrout}

 Gen2 Mean AFI difference scores were also reliable (r = 0.734) and comparable to Generation 1 sibling differences.
%%%%%%%%%%%% Results %%%%%%%%%%%%
\section{Results}
\input{../Common/content/results/results.txt}
%
% Between Family
\subsection{Between Family}
\input{../Common/content/results/results_between.txt}
%
% Within Family
\subsection{Within Family}
\input{../Common/content/results/results_within.txt}
%
%%%%%%%%%%%% Discussion %%%%%%%%%%%%
\section{Discussion}
\input{../Common/content/discussion/discussion.txt}

@@

\end{knitrout}
\end{center}
\pagebreak
%
\begin{center}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=1.1\paperwidth]{figure/plot_corplotmatrix_within-1}

\end{knitrout}
\captionof{figure}{Within Family Correlations}
\label{plot_within}
\end{center}
\pagebreak
%
\begin{center}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=1.1\paperwidth]{figure/plot_corplotmatrix_between-1}

\end{knitrout}
\captionof{figure}{Between Family Correlations}
\label{plot_between}
\end{center}
\pagebreak

\begin{center}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=.8\paperwidth]{figure/plot_spaghetti-1}

@@

\captionof{figure}{Spaghetti Plot. The mean Within-Family Slope is \ensuremath{-1.662}; the median Within-Family Slope is 0.055}
\label{plot_spaghetti}
